---
title: "AmObjects: Systematic data structures for AMARETTO"
author: "AMARETTO team"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{AMARETTO S4 Object Design Considerations}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Introduction

The general problem of multiomic data integration leads to
unusual situations of data volume, complexity, and annotation.
Metrics for comparing solutions are not readily available.

In the AmObjects package we use R's S4 object design
disciplines to hide complexity from end-users and to
provide hints so that model setup and results are easily
used in workflows that will evolve over time.

# Initializing the AMARETTO procedures

In the following, `iniobj` is a lossless representation
of the `TCGA-LIHC_AMARETTOinit` constructed as a
small test case.
```{r chk1}
library(AmObjects)
origlist = AmObjects::LIHC_AMARETTOinit
names(origlist)
iniobj = AmInit(origlist)
iniobj
```

# Representing AMARETTO results

```{r chk2}
reslist = AmObjects::LIHC_AMARETTOresults
names(reslist)
resobj = AmResults(reslist)
resobj
```
